Total Amount of Vaccinations by Age Among Black population in the Target Zip Codes

### 2023-04-05 code/analysis_code/analysiscode.qmd
Part 4

---
title: "Total Amount of Vaccinations Among African Americans in the Target Zip Codes"
format: html
editor: visual
echo: FALSE 
---

@@

# Analysis of the Amount of Vaccinations Among African Americans in Each Target Zip Code

@@

### Saving the combined data for African Americans for future use. Will be useful when stratifying the African American population by age and gender

@@

### Dropping all variables except for total black variables in order to obtain vaccination rates of all African Americans in the 31701 zip code

#### Using the select() function to subset the data frame by columns that start with "total_black_vax" which are variables with a total count of African Americans with at least one dose of the COVID-19 vaccine by month

@@

### gglot2: Creating a line plot for the vaccination totals by month for the African American population in the 31701 zip code 
```{r}
plot_31701_total_black_vax = Sum_by_month_31701 %>% 
  ggplot(aes(Date, Total, group=1)) + 
  geom_point() + geom_line() + 
  scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))

#Adding a customization title for the plot 
plot_31701_total_black_vax = plot_31701_total_black_vax + 
  ggtitle("Vaccination Totals for African Americans in the 31701 Zipcode") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic"))
```

@@

### Loading the processed data in order to begin analysis for the 31705 zip code
```{r}
#Loading September 31705
data_location7 = here("data", "processed_data", "Zip_31705", "processed_data_31705_Sept.rds")
processed_data_31705_Sept = readRDS(data_location7)

@@

### Saving the combined data for African Americans for future use 
```{r}
save_data_location = here("data", "processed_data","Zip_31705", "processed_combined_31705.rds")
saveRDS(processed_combined_31705, file = save_data_location)
```

### Dropping all variables except for total black variables in order to obtain vaccination rates of all African Americans in the 31705 zip code 
```{r}
processed_combined_31705_total_black = processed_combined_31705 %>% select(starts_with("total_black_vax"))
```

### Summing each column for each month 
```{r}

@@

### Total contains the vaccination totals for each month
```{r}
Sum_by_month_31705 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                                Total = c(10383, 10327, 10303, 10301, 10337, 10348)) 
```

### ggplot creating a line plot for the vaccination totals by month for the 31705 zip code African American population
```{r}
plot_31705_total_black_vax = Sum_by_month_31705 %>% 
  ggplot(aes(Date, Total, group=1)) + 
  geom_point() + geom_line() + 
  scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))

#Adding a customization title for the plot 
plot_31705_total_black_vax = plot_31705_total_black_vax + 
  ggtitle("Vaccination Totals for African Americans in the 31705 Zipcode") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic"))
```

@@

### Loading the processed data in order to begin analysis for the 31707 zip code
```{r}
# Loading September 31707
data_location13 = here("data", "processed_data", "Zip_31707", "processed_data_31707_Sept.rds")
processed_data_31707_Sept = readRDS(data_location13)

@@

### Saving the combined data for African Americans for future use 
```{r}
save_data_location = here("data", "processed_data","Zip_31707", "processed_combined_31707.rds")
saveRDS(processed_combined_31707, file = save_data_location)
```

### Dropping all variables except for total black variables in order to obtain vaccination rates of all African Americans in the 31707 zip code 
```{r}
processed_combined_31707_total_black = processed_combined_31707 %>% select(starts_with("total_black_vax"))

@@

### Summing each column for each month 
```{r}
sum(processed_combined_31707_total_black$total_black_vax_Sept_17) 
sum(processed_combined_31707_total_black$total_black_vax_Oct_28) 
sum(processed_combined_31707_total_black$total_black_vax_Nov_24) 
sum(processed_combined_31707_total_black$total_black_vax_Dec_29) 
sum(processed_combined_31707_total_black$total_black_vax_Jan_26) 
sum(processed_combined_31707_total_black$total_black_vax_Feb_26)
```

### Separating sums by month into a data fram consisting of two variables: Date and Total 
### Date contains months September-February
### Total contains the vaccination totals for each month
```{r}
Sum_by_month_31707 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                                Total = c(9035, 8985, 8997, 9005, 9035, 9042))

@@

###ggplot: creating a line plot for the vaccination totals by month for the 31707 zip code African American population
```{r}
plot_31707_total_black_vax = Sum_by_month_31707 %>% 
  ggplot(aes(Date, Total, group=1)) + 
  geom_point() + geom_line() + 
  scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))

#Adding a customization title for the plot
plot_31707_total_black_vax = plot_31707_total_black_vax + 
  ggtitle("Vaccination Totals for African Americans in the 31707 Zipcode") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic"))
```

@@

### Taking a look at each of the line plots for the different zip codes and comparing the total vaccinations by month in the African American population 
```{r}
plot_31701_total_black_vax
plot_31705_total_black_vax
plot_31707_total_black_vax
```

### Combining all plots into one
```{r}
## Creating a new dataframe called "Total_black_vax" by combining the vaccination totals from 31701 and 3105 by using leftjoin() by the Date variable 
Total_black_vax = left_join(Sum_by_month_31701, Sum_by_month_31705, by = c("Date" = "Date"))

@@

### Combining the new dataframe "Total_black_vax" with the 31707 zip vaccination totals so all three target zip codes are in the same data frame 
```{r}
Total_black_vax = left_join(Total_black_vax, Sum_by_month_31707, by = c("Date" = "Date"))
```

### Renaming column totals to match the zip
### Haing to do this because the the total variable names are Total.x, Total.y and Total
### Need to specificy each total variable by zip using the following code
```{r}
Total_black_vax <- Total_black_vax %>% 
  rename("31701" = "Total.x") %>% 
  rename("31705" = "Total.y") %>%
  rename("31707" = "Total")
```

### Converting data to long format in order to create a line plot using ggplot
```{r}
Total_black_vax_long = reshape2::melt(Total_black_vax, id = "Date")
```

### Changing the variable name "variable" to "Zip_code" and "value" to "Vaccination_total" for clarity
### Doing this because when the data was converted to a long format the column names we changed to "variable" which refers to the zip code and "value" which refers to the amount of vaccinations
### Changing "variable" to "Zip_code" and "value" to "Vaccination_total"
```{r}
Total_black_vax_long <- Total_black_vax_long %>% 
  rename("Zip_code" = "variable") %>% 
  rename("Vaccination_total" = "value")
```

### ggplot: Making a line graph that compares the vaccination totals for each African American population in each zip code
```{r}
plot_Total_black_vax = Total_black_vax_long %>% 
                     ggplot(aes(Date, Vaccination_total, 
                                group = Zip_code, 
                                color = Zip_code)) + 
                     geom_point() + geom_line() + 
                     scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))
#adding a title to the plot 
plot_Total_black_vax = plot_Total_black_vax + 
  ggtitle("Vaccination Totals for African Americans in Target Zip Codes") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic")) + 
  labs(y = "Vaccination Total")
plot_Total_black_vax
```

### Turning ggplot into an interactive plot
```{r}
plotly_Total_black_vax = ggplotly(plot_Total_black_vax)
plotly_Total_black_vax
```

>>>>

---
title: "Total Amount of Vaccinations Among Black population in the Target Zip Codes"
output: 
  html_document
echo: FALSE 
---

@@

# Analysis of the Amount of Vaccinations Among Black population in Each Target Zip Code

@@

### Saving the combined data for Black population for future use. Will be useful when stratifying the African American population by age and gender

@@

### Dropping all variables except for total black variables in order to obtain vaccination rates of all Black population in the 31701 zip code

#### Using the select() function to subset the data frame by columns that start with "total_black_vax" which are variables with a total count of Black population with at least one dose of the COVID-19 vaccine by month

@@

### gglot2: Creating a line plot for the vaccination totals by month for the African American population in the 31701 zip code

```{r}
plot_31701_total_black_vax = Sum_by_month_31701 %>% 
  ggplot(aes(Date, Total, group=1)) + 
  geom_point() + geom_line() + 
  scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))

#Adding a customization title for the plot 
plot_31701_total_black_vax = plot_31701_total_black_vax + 
  ggtitle("Vaccination Totals for Black population in the 31701 Zipcode") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic"))
```

@@

### Loading the processed data in order to begin analysis for the 31705 zip code

```{r}
#Loading September 31705
data_location7 = here("data", "processed_data", "Zip_31705", "processed_data_31705_Sept.rds")
processed_data_31705_Sept = readRDS(data_location7)

@@

### Saving the combined data for Black population for future use

```{r}
save_data_location = here("data", "processed_data","Zip_31705", "processed_combined_31705.rds")
saveRDS(processed_combined_31705, file = save_data_location)
```

### Dropping all variables except for total black variables in order to obtain vaccination rates of all Black population in the 31705 zip code

```{r}
processed_combined_31705_total_black = processed_combined_31705 %>% select(starts_with("total_black_vax"))
```

### Summing each column for each month

```{r}

@@

### Total contains the vaccination totals for each month

```{r}
Sum_by_month_31705 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                                Total = c(10383, 10327, 10303, 10301, 10337, 10348)) 
```

### ggplot creating a line plot for the vaccination totals by month for the 31705 zip code African American population

```{r}
plot_31705_total_black_vax = Sum_by_month_31705 %>% 
  ggplot(aes(Date, Total, group=1)) + 
  geom_point() + geom_line() + 
  scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))

#Adding a customization title for the plot 
plot_31705_total_black_vax = plot_31705_total_black_vax + 
  ggtitle("Vaccination Totals for Black population in the 31705 Zipcode") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic"))
```

@@

### Loading the processed data in order to begin analysis for the 31707 zip code

```{r}
# Loading September 31707
data_location13 = here("data", "processed_data", "Zip_31707", "processed_data_31707_Sept.rds")
processed_data_31707_Sept = readRDS(data_location13)

@@

### Saving the combined data for Black population for future use

```{r}
save_data_location = here("data", "processed_data","Zip_31707", "processed_combined_31707.rds")
saveRDS(processed_combined_31707, file = save_data_location)
```

### Dropping all variables except for total black variables in order to obtain vaccination rates of all Black population in the 31707 zip code

```{r}
processed_combined_31707_total_black = processed_combined_31707 %>% select(starts_with("total_black_vax"))

@@

### Summing each column for each month

```{r}
sum(processed_combined_31707_total_black$total_black_vax_Sept_17) 
sum(processed_combined_31707_total_black$total_black_vax_Oct_28) 
sum(processed_combined_31707_total_black$total_black_vax_Nov_24) 
sum(processed_combined_31707_total_black$total_black_vax_Dec_29) 
sum(processed_combined_31707_total_black$total_black_vax_Jan_26) 
sum(processed_combined_31707_total_black$total_black_vax_Feb_26)
```

### Total contains the vaccination totals for each month

```{r}
Sum_by_month_31707 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                                Total = c(9035, 8985, 8997, 9005, 9035, 9042))

@@

###ggplot: creating a line plot for the vaccination totals by month for the 31707 zip code African American population

```{r}
plot_31707_total_black_vax = Sum_by_month_31707 %>% 
  ggplot(aes(Date, Total, group=1)) + 
  geom_point() + geom_line() + 
  scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))

#Adding a customization title for the plot
plot_31707_total_black_vax = plot_31707_total_black_vax + 
  ggtitle("Vaccination Totals for Black population in the 31707 Zipcode") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic"))
```

@@

### Taking a look at each of the line plots for the different zip codes and comparing the total vaccinations by month in the African American population

```{r}
plot_31701_total_black_vax
plot_31705_total_black_vax
plot_31707_total_black_vax
```

### Combining all plots into one

```{r}
## Creating a new dataframe called "Total_black_vax" by combining the vaccination totals from 31701 and 3105 by using leftjoin() by the Date variable 
Total_black_vax = left_join(Sum_by_month_31701, Sum_by_month_31705, by = c("Date" = "Date"))

@@

### Combining the new dataframe "Total_black_vax" with the 31707 zip vaccination totals so all three target zip codes are in the same data frame

```{r}
Total_black_vax = left_join(Total_black_vax, Sum_by_month_31707, by = c("Date" = "Date"))
```

### Renaming column totals to match the zip

### Haing to do this because the the total variable names are Total.x, Total.y and Total

### Need to specificy each total variable by zip using the following code

```{r}
Total_black_vax <- Total_black_vax %>% 
  rename("31701" = "Total.x") %>% 
  rename("31705" = "Total.y") %>%
  rename("31707" = "Total")
```

### Converting data to long format in order to create a line plot using ggplot

```{r}
Total_black_vax_long = reshape2::melt(Total_black_vax, id = "Date")
```

### Changing the variable name "variable" to "Zip_code" and "value" to "Vaccination_total" for clarity

### Doing this because when the data was converted to a long format the column names we changed to "variable" which refers to the zip code and "value" which refers to the amount of vaccinations

### Changing "variable" to "Zip_code" and "value" to "Vaccination_total"

```{r}
Total_black_vax_long <- Total_black_vax_long %>% 
  rename("Zip_code" = "variable") %>% 
  rename("Vaccination_total" = "value")
```

### ggplot: Making a line graph that compares the vaccination totals for each African American population in each zip code

```{r}
plot_Total_black_vax = Total_black_vax_long %>% 
                     ggplot(aes(Date, Vaccination_total, 
                                group = Zip_code, 
                                color = Zip_code)) + 
                     geom_point() + geom_line() + 
                     scale_x_discrete(limits = c("Sep","Oct","Nov","Dec","Jan","Feb"))
#adding a title to the plot 
plot_Total_black_vax = plot_Total_black_vax + 
  ggtitle("Vaccination Totals for Black population in Target Zip Codes") + 
  theme(plot.title = 
          element_text(color="red", size=10, face="bold.italic")) + 
  labs(y = "Vaccination Total")
plot_Total_black_vax
```

### Turning ggplot into an interactive plot

```{r}
plotly_Total_black_vax = ggplotly(plot_Total_black_vax)
plotly_Total_black_vax
```

### 2023-04-05 code/analysis_code/analysiscode3.qmd
Part 4

---
title: "Total Amount of Vaccinations by Gender Among Black population in the Target Zip Codes"
output: 
  html_document
echo: FALSE 
---

@@

```{r}
processed_combined_31701_Gender_black = processed_combined_31701 %>% select(matches("^total_(mblack|fblack)_vax"))
```

@@

# Thoughts regarding exploratory analysis 
In each zip code there is a large gap between females that are Black and males that are Black. I am pretty taken back by how large the gap is.

>>>>

---
title: "Total Amount of Vaccinations by Age Among Black population in the Target Zip Codes"
output: 
  html_document
echo: FALSE 
---

@@

```{r}
processed_combined_31701_Age_black = processed_combined_31701 %>% 
  select(starts_with("total_05_09"), starts_with("total_10_17"), starts_with("total_18_44"), starts_with("total_45_64"), starts_with("total_65Plus"))
```

@@
